---
title: "tvARMA report"
author: "Shu Wei"
date: ""
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,fig.width=7, fig.height=7)
```

## tvARMA(1,1) with tempered stable

```{r, echo=FALSE}
library(car)
library(forecast)
library(moments)
```

Loading simulation results:

```{r}
load("./results/tvARMA_simulation_0_2_T500.Rdata")
resultsA1T1<-results
load("./results/tvARMA_simulation_0_2_T1000.Rdata")
resultsA1T2<-results
load("./results/tvARMA_simulation_0_2_T1500.Rdata")
resultsA1T3<-results
load("./results/tvARMA_simulation_0_2_T2000.Rdata")
resultsA1T4<-results
load("./results/tvARMA_simulation_0_2_T3000.Rdata")
resultsA1T5<-results

load("./results/tvARMA_simulation_0_3_T500.Rdata")
resultsA2T1<-results
load("./results/tvARMA_simulation_0_3_T1000.Rdata")
resultsA2T2<-results
load("./results/tvARMA_simulation_0_3_T1500.Rdata")
resultsA2T3<-results
load("./results/tvARMA_simulation_0_3_T2000.Rdata")
resultsA2T4<-results
load("./results/tvARMA_simulation_0_3_T3000.Rdata")
resultsA2T5<-results

load("./results/tvARMA_simulation_0_7_T500.Rdata")
resultsA3T1<-results
load("./results/tvARMA_simulation_0_7_T1000.Rdata")
resultsA3T2<-results
load("./results/tvARMA_simulation_0_7_T1500.Rdata")
resultsA3T3<-results
load("./results/tvARMA_simulation_0_7_T2000.Rdata")
resultsA3T4<-results
load("./results/tvARMA_simulation_0_7_T3000.Rdata")
resultsA3T5<-results

parametrosA1<-c(0.2,1,1,0.3,-0.3,-0.5,0.4,1.2)
parametrosA2<-c(0.3,0.5,1,-0.3,0.8,0.5,-0.1,1)
parametrosA3<-c(0.7,1,0.5,0.3,-0.3,-0.5,0.4,1.2)
```

Functions:

```{r}
mean.sd<-function(y){
  tabla<-as.matrix(c(mean(y),sd(y)))
  rownames(tabla)<-c("mean","sd")
  return(tabla)
}
kurtosis.skewness<-function(y){
  tabla<-as.matrix(c(kurtosis(y),skewness(y)))
  return(tabla)
}
```


## Scenario 1

$\alpha=0.2$,\
$\lambda_+=1$,\
$\lambda_-=1$,\
$\theta_{a0}=0.3$\
$\theta_{a1}=-0.3$\
$\theta_{b0}=-0.5$\
$\theta_{b1}=0.4$\
$\gamma=1.2$.\

```{r}
tablaA1T1<-apply(resultsA1T1,2,mean.sd)
tablaA1T2<-apply(resultsA1T2,2,mean.sd)
tablaA1T3<-apply(resultsA1T3,2,mean.sd)
tablaA1T4<-apply(resultsA1T4,2,mean.sd)
tablaA1T5<-apply(resultsA1T5,2,mean.sd)
tablaA1a<-rbind(tablaA1T1,tablaA1T2,tablaA1T3,tablaA1T4,tablaA1T5)
row.names(tablaA1a)<-c("T1.mean","sd","T2.mean","sd","T3mean","sd","T4mean","sd","T5mean","sd")
round(tablaA1a,4)
parametrosA1
```


```{r}
tablaA1T1<-apply(resultsA1T1,2,kurtosis.skewness)
tablaA1T2<-apply(resultsA1T2,2,kurtosis.skewness)
tablaA1T3<-apply(resultsA1T3,2,kurtosis.skewness)
tablaA1T4<-apply(resultsA1T4,2,kurtosis.skewness)
tablaA1T5<-apply(resultsA1T5,2,kurtosis.skewness)
rownames(tablaA1T1)<-c("kurtosis","skewness")
rownames(tablaA1T2)<-c("kurtosis","skewness")
rownames(tablaA1T3)<-c("kurtosis","skewness")
rownames(tablaA1T4)<-c("kurtosis","skewness")
rownames(tablaA1T5)<-c("kurtosis","skewness")
tablaA1b<-rbind(tablaA1T1,tablaA1T2,tablaA1T3,tablaA1T4,tablaA1T5)
round(tablaA1b,4)
```


Density estimates

```{r,fig.width=10, fig.height=10}
par(mfrow=c(3,3))
plot(density(resultsA1T1[,1],adjust = 1.5),lty=1,col=2,ylim=c(0,6),xlab=expression(alpha),main="", cex.lab = 1.5)
points(density(resultsA1T2[,1],adjust = 1.5),type="l",lty=4,col=3)
points(density(resultsA1T3[,1],adjust = 1.5),type="l",lty=5,col=4)
points(density(resultsA1T4[,1],adjust = 1.5),type="l",lty=6,col=5)
points(density(resultsA1T5[,1],adjust = 1.5),type="l",lty=7,col=8)
abline(v=parametrosA1[1],col=6)
legend("topright",c("T=500","T=1000","T=1500","T=2000"),lty=c(1,4,5,6,7),col=c(2,3,4,5,6))

plot(density(resultsA1T1[,2],adjust = 1.5),lty=1,col=2,ylim=c(0,4),xlab="lambda.p",main="", cex.lab = 1.5)
points(density(resultsA1T2[,2],adjust = 1.5),type="l",lty=4,col=3)
points(density(resultsA1T3[,2],adjust = 1.5),type="l",lty=5,col=4)
points(density(resultsA1T4[,2],adjust = 1.5),type="l",lty=6,col=5)
points(density(resultsA1T5[,2],adjust = 1.5),type="l",lty=7,col=8)
abline(v=parametrosA1[2],col=6)
legend("topright",c("T=500","T=1000","T=1500","T=2000"),lty=c(1,4,5,6,7),col=c(2,3,4,5,6))

plot(density(resultsA1T1[,3],adjust = 1.5),lty=1,col=2,ylim=c(0,4),xlab="lambda.n",main="", cex.lab = 1.5)
points(density(resultsA1T2[,3],adjust = 1.5),type="l",lty=4,col=3)
points(density(resultsA1T3[,3],adjust = 1.5),type="l",lty=5,col=4)
points(density(resultsA1T4[,3],adjust = 1.5),type="l",lty=6,col=5)
points(density(resultsA1T5[,3],adjust = 1.5),type="l",lty=7,col=8)
abline(v=parametrosA1[3],col=6)
legend("topright",c("T=500","T=1000","T=1500","T=2000"),lty=c(1,4,5,6,7),col=c(2,3,4,5,6))

plot(density(resultsA1T1[,4],adjust = 1.5),lty=1,col=2,ylim=c(0,6),xlab=expression(theta[00]),main="", cex.lab = 1.5)
points(density(resultsA1T2[,4],adjust = 1.5),type="l",lty=4,col=3)
points(density(resultsA1T3[,4],adjust = 1.5),type="l",lty=5,col=4)
points(density(resultsA1T4[,4],adjust = 1.5),type="l",lty=6,col=5)
points(density(resultsA1T5[,4],adjust = 1.5),type="l",lty=7,col=8)
abline(v=parametrosA1[4],col=6)
legend("topright",c("T=500","T=1000","T=1500","T=2000"),lty=c(1,4,5,6,7),col=c(2,3,4,5,6))

plot(density(resultsA1T1[,5],adjust = 1.5),lty=1,col=2,ylim=c(0,2.5),xlab=expression(theta[01]),main="", cex.lab = 1.5)
points(density(resultsA1T2[,5],adjust = 1.5),type="l",lty=4,col=3)
points(density(resultsA1T3[,5],adjust = 1.5),type="l",lty=5,col=4)
points(density(resultsA1T4[,5],adjust = 1.5),type="l",lty=6,col=5)
points(density(resultsA1T5[,5],adjust = 1.5),type="l",lty=7,col=8)
abline(v=parametrosA1[5],col=6)
legend("topright",c("T=500","T=1000","T=1500","T=2000"),lty=c(1,4,5,6,7),col=c(2,3,4,5,6))

plot(density(resultsA1T1[,6],adjust = 1.5),lty=1,col=2,ylim=c(0,6),xlab=expression(theta[10]),main="", cex.lab = 1.5)
points(density(resultsA1T2[,6],adjust = 1.5),type="l",lty=4,col=3)
points(density(resultsA1T3[,6],adjust = 1.5),type="l",lty=5,col=4)
points(density(resultsA1T4[,6],adjust = 1.5),type="l",lty=6,col=5)
points(density(resultsA1T5[,6],adjust = 1.5),type="l",lty=7,col=8)
abline(v=parametrosA1[6],col=6)
legend("topright",c("T=500","T=1000","T=1500","T=2000"),lty=c(1,4,5,6,7),col=c(2,3,4,5,6))

plot(density(resultsA1T1[,7],adjust = 1.5),lty=1,col=2,ylim=c(0,3),xlab=expression(theta[11]),main="", cex.lab = 1.5)
points(density(resultsA1T2[,7],adjust = 1.5),type="l",lty=4,col=3)
points(density(resultsA1T3[,7],adjust = 1.5),type="l",lty=5,col=4)
points(density(resultsA1T4[,7],adjust = 1.5),type="l",lty=6,col=5)
points(density(resultsA1T5[,7],adjust = 1.5),type="l",lty=7,col=8)
abline(v=parametrosA1[7],col=6)
legend("topright",c("T=500","T=1000","T=1500","T=2000"),lty=c(1,4,5,6,7),col=c(2,3,4,5,6))

plot(density(resultsA1T1[,8],adjust = 1.5),lty=1,col=2,ylim=c(0,15),xlab=expression(gamma),main="", cex.lab = 1.5)
points(density(resultsA1T2[,8],adjust = 1.5),type="l",lty=4,col=3)
points(density(resultsA1T3[,8],adjust = 1.5),type="l",lty=5,col=4)
points(density(resultsA1T4[,8],adjust = 1.5),type="l",lty=6,col=5)
points(density(resultsA1T5[,8],adjust = 1.5),type="l",lty=7,col=8)
abline(v=parametrosA1[8],col=6)
legend("topright",c("T=500","T=1000","T=1500","T=2000"),lty=c(1,4,5,6,7),col=c(2,3,4,5,6))
```



##Eliminating the outlier

```{r}
resultsA1T1<-resultsA1T1[(resultsA1T1[,2]<2 &resultsA1T1[,3]<2),]
resultsA1T2<-resultsA1T2[(resultsA1T2[,2]<2 &resultsA1T2[,3]<2),]
resultsA1T3<-resultsA1T3[(resultsA1T3[,2]<2 &resultsA1T3[,3]<2),]
resultsA1T4<-resultsA1T4[(resultsA1T4[,2]<2 &resultsA1T4[,3]<2),]
resultsA1T5<-resultsA1T5[(resultsA1T5[,2]<2 &resultsA1T5[,3]<2),]
dim(resultsA1T1)
dim(resultsA1T2)
dim(resultsA1T3)
dim(resultsA1T4)
dim(resultsA1T5)
```



```{r}
tablaA1T1<-apply(resultsA1T1,2,mean.sd)
tablaA1T2<-apply(resultsA1T2,2,mean.sd)
tablaA1T3<-apply(resultsA1T3,2,mean.sd)
tablaA1T4<-apply(resultsA1T4,2,mean.sd)
tablaA1T5<-apply(resultsA1T5,2,mean.sd)
tablaA1a<-rbind(tablaA1T1,tablaA1T2,tablaA1T3,tablaA1T4,tablaA1T5)
row.names(tablaA1a)<-c("T1.mean","sd","T2.mean","sd","T3mean","sd","T4mean","sd","T5mean","sd")
round(tablaA1a,4)
parametrosA1
```


```{r}
tablaA1T1<-apply(resultsA1T1,2,kurtosis.skewness)
tablaA1T2<-apply(resultsA1T2,2,kurtosis.skewness)
tablaA1T3<-apply(resultsA1T3,2,kurtosis.skewness)
tablaA1T4<-apply(resultsA1T4,2,kurtosis.skewness)
tablaA1T5<-apply(resultsA1T5,2,kurtosis.skewness)
rownames(tablaA1T1)<-c("kurtosis","skewness")
rownames(tablaA1T2)<-c("kurtosis","skewness")
rownames(tablaA1T3)<-c("kurtosis","skewness")
rownames(tablaA1T4)<-c("kurtosis","skewness")
rownames(tablaA1T5)<-c("kurtosis","skewness")
tablaA1b<-rbind(tablaA1T1,tablaA1T2,tablaA1T3,tablaA1T4,tablaA1T5)
round(tablaA1b,4)
```

Density estimates

```{r,fig.width=10, fig.height=10}
par(mfrow=c(3,3))
plot(density(resultsA1T1[,1],adjust = 1.5),lty=1,col=2,ylim=c(0,6),xlab=expression(alpha),main="", cex.lab = 1.5)
points(density(resultsA1T2[,1],adjust = 1.5),type="l",lty=4,col=3)
points(density(resultsA1T3[,1],adjust = 1.5),type="l",lty=5,col=4)
points(density(resultsA1T4[,1],adjust = 1.5),type="l",lty=6,col=5)
points(density(resultsA1T5[,1],adjust = 1.5),type="l",lty=7,col=8)
abline(v=parametrosA1[1],col=6)
legend("topright",c("T=500","T=1000","T=1500","T=2000"),lty=c(1,4,5,6,7),col=c(2,3,4,5,6))

plot(density(resultsA1T1[,2],adjust = 1.5),lty=1,col=2,ylim=c(0,4),xlab="lambda.p",main="", cex.lab = 1.5)
points(density(resultsA1T2[,2],adjust = 1.5),type="l",lty=4,col=3)
points(density(resultsA1T3[,2],adjust = 1.5),type="l",lty=5,col=4)
points(density(resultsA1T4[,2],adjust = 1.5),type="l",lty=6,col=5)
points(density(resultsA1T5[,2],adjust = 1.5),type="l",lty=7,col=8)
abline(v=parametrosA1[2],col=6)
legend("topright",c("T=500","T=1000","T=1500","T=2000"),lty=c(1,4,5,6,7),col=c(2,3,4,5,6))

plot(density(resultsA1T1[,3],adjust = 1.5),lty=1,col=2,ylim=c(0,4),xlab="lambda.n",main="", cex.lab = 1.5)
points(density(resultsA1T2[,3],adjust = 1.5),type="l",lty=4,col=3)
points(density(resultsA1T3[,3],adjust = 1.5),type="l",lty=5,col=4)
points(density(resultsA1T4[,3],adjust = 1.5),type="l",lty=6,col=5)
points(density(resultsA1T5[,3],adjust = 1.5),type="l",lty=7,col=8)
abline(v=parametrosA1[3],col=6)
legend("topright",c("T=500","T=1000","T=1500","T=2000"),lty=c(1,4,5,6,7),col=c(2,3,4,5,6))

plot(density(resultsA1T1[,4],adjust = 1.5),lty=1,col=2,ylim=c(0,6),xlab=expression(theta[00]),main="", cex.lab = 1.5)
points(density(resultsA1T2[,4],adjust = 1.5),type="l",lty=4,col=3)
points(density(resultsA1T3[,4],adjust = 1.5),type="l",lty=5,col=4)
points(density(resultsA1T4[,4],adjust = 1.5),type="l",lty=6,col=5)
points(density(resultsA1T5[,4],adjust = 1.5),type="l",lty=7,col=8)
abline(v=parametrosA1[4],col=6)
legend("topright",c("T=500","T=1000","T=1500","T=2000"),lty=c(1,4,5,6,7),col=c(2,3,4,5,6))

plot(density(resultsA1T1[,5],adjust = 1.5),lty=1,col=2,ylim=c(0,2.5),xlab=expression(theta[01]),main="", cex.lab = 1.5)
points(density(resultsA1T2[,5],adjust = 1.5),type="l",lty=4,col=3)
points(density(resultsA1T3[,5],adjust = 1.5),type="l",lty=5,col=4)
points(density(resultsA1T4[,5],adjust = 1.5),type="l",lty=6,col=5)
points(density(resultsA1T5[,5],adjust = 1.5),type="l",lty=7,col=8)
abline(v=parametrosA1[5],col=6)
legend("topright",c("T=500","T=1000","T=1500","T=2000"),lty=c(1,4,5,6,7),col=c(2,3,4,5,6))

plot(density(resultsA1T1[,6],adjust = 1.5),lty=1,col=2,ylim=c(0,6),xlab=expression(theta[10]),main="", cex.lab = 1.5)
points(density(resultsA1T2[,6],adjust = 1.5),type="l",lty=4,col=3)
points(density(resultsA1T3[,6],adjust = 1.5),type="l",lty=5,col=4)
points(density(resultsA1T4[,6],adjust = 1.5),type="l",lty=6,col=5)
points(density(resultsA1T5[,6],adjust = 1.5),type="l",lty=7,col=8)
abline(v=parametrosA1[6],col=6)
legend("topright",c("T=500","T=1000","T=1500","T=2000"),lty=c(1,4,5,6,7),col=c(2,3,4,5,6))

plot(density(resultsA1T1[,7],adjust = 1.5),lty=1,col=2,ylim=c(0,3),xlab=expression(theta[11]),main="", cex.lab = 1.5)
points(density(resultsA1T2[,7],adjust = 1.5),type="l",lty=4,col=3)
points(density(resultsA1T3[,7],adjust = 1.5),type="l",lty=5,col=4)
points(density(resultsA1T4[,7],adjust = 1.5),type="l",lty=6,col=5)
points(density(resultsA1T5[,7],adjust = 1.5),type="l",lty=7,col=8)
abline(v=parametrosA1[7],col=6)
legend("topright",c("T=500","T=1000","T=1500","T=2000"),lty=c(1,4,5,6,7),col=c(2,3,4,5,6))

plot(density(resultsA1T1[,8],adjust = 1.5),lty=1,col=2,ylim=c(0,15),xlab=expression(gamma),main="", cex.lab = 1.5)
points(density(resultsA1T2[,8],adjust = 1.5),type="l",lty=4,col=3)
points(density(resultsA1T3[,8],adjust = 1.5),type="l",lty=5,col=4)
points(density(resultsA1T4[,8],adjust = 1.5),type="l",lty=6,col=5)
points(density(resultsA1T5[,8],adjust = 1.5),type="l",lty=7,col=8)
abline(v=parametrosA1[8],col=6)
legend("topright",c("T=500","T=1000","T=1500","T=2000"),lty=c(1,4,5,6,7),col=c(2,3,4,5,6))
```





For t=500:

```{r,fig.width=15, fig.height=15}
par(mfrow=c(3,3))
for(i in 1:3){
  hist(resultsA1T1[,i],freq=FALSE,xlab=expression(theta[i]),main="", cex.lab = 1.5,breaks=20)
  abline(v=parametrosA1[i],col=3)
  curve(dnorm(x,mean(resultsA1T1[,i]),sd(resultsA1T1[,i])),add=T,col=2)
  qqPlot(resultsA1T1[,i])
  boxplot(resultsA1T1[,i])
}
```

For t=1000:

```{r,fig.width=15, fig.height=15}
par(mfrow=c(3,3))
for(i in 1:3){
  hist(resultsA1T2[,i],freq=FALSE,xlab=expression(theta[i]),main="", cex.lab = 1.5,breaks=20)
  abline(v=parametrosA1[i],col=3)
  curve(dnorm(x,mean(resultsA1T2[,i]),sd(resultsA1T2[,i])),add=T,col=2)
  qqPlot(resultsA1T2[,i])
  boxplot(resultsA1T2[,i])
}
```

For t=1500:

```{r,fig.width=15, fig.height=15}
par(mfrow=c(3,3))
for(i in 1:3){
  hist(resultsA1T3[,i],freq=FALSE,xlab=expression(theta[i]),main="", cex.lab = 1.5,breaks=20)
  abline(v=parametrosA1[i],col=3)
  curve(dnorm(x,mean(resultsA1T3[,i]),sd(resultsA1T3[,i])),add=T,col=2)
  qqPlot(resultsA1T3[,i])
  boxplot(resultsA1T3[,i])
}
```

For t=2000:

```{r,fig.width=15, fig.height=15}
par(mfrow=c(3,3))
for(i in 1:3){
  hist(resultsA1T4[,i],freq=FALSE,xlab=expression(theta[i]),main="", cex.lab = 1.5,breaks=20)
  abline(v=parametrosA1[i],col=3)
  curve(dnorm(x,mean(resultsA1T4[,i]),sd(resultsA1T4[,i])),add=T,col=2)
  qqPlot(resultsA1T4[,i])
  boxplot(resultsA1T4[,i])
}
```
For t=3000:

```{r,fig.width=15, fig.height=15}
par(mfrow=c(3,3))
for(i in 1:3){
  hist(resultsA1T5[,i],freq=FALSE,xlab=expression(theta[i]),main="", cex.lab = 1.5,breaks=20)
  abline(v=parametrosA1[i],col=3)
  curve(dnorm(x,mean(resultsA1T5[,i]),sd(resultsA1T5[,i])),add=T,col=2)
  qqPlot(resultsA1T5[,i])
  boxplot(resultsA1T5[,i])
}
```

## Scenario 2

$\alpha=0.3$,\
$\lambda_+=0.5$,\
$\lambda_-=1$,\
$\theta_{a0}=-0.3$\
$\theta_{a1}=0.8$\
$\theta_{b0}=0.5$\
$\theta_{b1}=-0.1$\
$\gamma=1$.\


```{r}
tablaA2T1<-apply(resultsA2T1,2,mean.sd)
tablaA2T2<-apply(resultsA2T2,2,mean.sd)
tablaA2T3<-apply(resultsA2T3,2,mean.sd)
tablaA2T4<-apply(resultsA2T4,2,mean.sd)
tablaA2T5<-apply(resultsA2T5,2,mean.sd)
tablaA2a<-rbind(tablaA2T1,tablaA2T2,tablaA2T3,tablaA2T4,tablaA2T5)
row.names(tablaA2a)<-c("T1.mean","sd","T2.mean","sd","T3mean","sd","T4mean","sd","T5mean","sd")
round(tablaA2a,4)
parametrosA2
```


```{r}
tablaA2T1<-apply(resultsA2T1,2,kurtosis.skewness)
tablaA2T2<-apply(resultsA2T2,2,kurtosis.skewness)
tablaA2T3<-apply(resultsA2T3,2,kurtosis.skewness)
tablaA2T4<-apply(resultsA2T4,2,kurtosis.skewness)
tablaA2T5<-apply(resultsA2T5,2,kurtosis.skewness)
rownames(tablaA2T1)<-c("kurtosis","skewness")
rownames(tablaA2T2)<-c("kurtosis","skewness")
rownames(tablaA2T3)<-c("kurtosis","skewness")
rownames(tablaA2T4)<-c("kurtosis","skewness")
rownames(tablaA2T5)<-c("kurtosis","skewness")
tablaA2b<-rbind(tablaA2T1,tablaA2T2,tablaA2T3,tablaA2T4,tablaA2T5)
round(tablaA2b,4)
```


Density estimates

```{r,fig.width=10, fig.height=10}
par(mfrow=c(3,3))
plot(density(resultsA2T1[,1],adjust = 1.5),lty=1,col=2,ylim=c(0,6),xlab=expression(alpha),main="", cex.lab = 1.5)
points(density(resultsA2T2[,1],adjust = 1.5),type="l",lty=4,col=3)
points(density(resultsA2T3[,1],adjust = 1.5),type="l",lty=5,col=4)
points(density(resultsA2T4[,1],adjust = 1.5),type="l",lty=6,col=5)
points(density(resultsA2T5[,1],adjust = 1.5),type="l",lty=7,col=8)
abline(v=parametrosA2[1],col=6)
legend("topright",c("T=500","T=1000","T=1500","T=2000"),lty=c(1,4,5,6,7),col=c(2,3,4,5,6))

plot(density(resultsA2T1[,2],adjust = 1.5),lty=1,col=2,ylim=c(0,6),xlab="lambda.p",main="", cex.lab = 1.5)
points(density(resultsA2T2[,2],adjust = 1.5),type="l",lty=4,col=3)
points(density(resultsA2T3[,2],adjust = 1.5),type="l",lty=5,col=4)
points(density(resultsA2T4[,2],adjust = 1.5),type="l",lty=6,col=5)
points(density(resultsA2T5[,2],adjust = 1.5),type="l",lty=7,col=8)
abline(v=parametrosA2[2],col=6)
legend("topright",c("T=500","T=1000","T=1500","T=2000"),lty=c(1,4,5,6,7),col=c(2,3,4,5,6))

plot(density(resultsA2T1[,3],adjust = 1.5),lty=1,col=2,ylim=c(0,6),xlab="lambda.n",main="", cex.lab = 1.5)
points(density(resultsA2T2[,3],adjust = 1.5),type="l",lty=4,col=3)
points(density(resultsA2T3[,3],adjust = 1.5),type="l",lty=5,col=4)
points(density(resultsA2T4[,3],adjust = 1.5),type="l",lty=6,col=5)
points(density(resultsA2T5[,3],adjust = 1.5),type="l",lty=7,col=8)
abline(v=parametrosA2[3],col=6)
legend("topright",c("T=500","T=1000","T=1500","T=2000"),lty=c(1,4,5,6,7),col=c(2,3,4,5,6))

plot(density(resultsA2T1[,4],adjust = 1.5),lty=1,col=2,ylim=c(0,5),xlab=expression(theta[00]),main="", cex.lab = 1.5)
points(density(resultsA2T2[,4],adjust = 1.5),type="l",lty=4,col=3)
points(density(resultsA2T3[,4],adjust = 1.5),type="l",lty=5,col=4)
points(density(resultsA2T4[,4],adjust = 1.5),type="l",lty=6,col=5)
points(density(resultsA2T5[,4],adjust = 1.5),type="l",lty=7,col=8)
abline(v=parametrosA2[4],col=6)
legend("topright",c("T=500","T=1000","T=1500","T=2000"),lty=c(1,4,5,6,7),col=c(2,3,4,5,6))

plot(density(resultsA2T1[,5],adjust = 1.5),lty=1,col=2,ylim=c(0,1.5),xlab=expression(theta[01]),main="", cex.lab = 1.5)
points(density(resultsA2T2[,5],adjust = 1.5),type="l",lty=4,col=3)
points(density(resultsA2T3[,5],adjust = 1.5),type="l",lty=5,col=4)
points(density(resultsA2T4[,5],adjust = 1.5),type="l",lty=6,col=5)
points(density(resultsA2T5[,5],adjust = 1.5),type="l",lty=7,col=8)
abline(v=parametrosA2[5],col=6)
legend("topright",c("T=500","T=1000","T=1500","T=2000"),lty=c(1,4,5,6,7),col=c(2,3,4,5,6))

plot(density(resultsA2T1[,6],adjust = 1.5),lty=1,col=2,ylim=c(0,5),xlab=expression(theta[10]),main="", cex.lab = 1.5)
points(density(resultsA2T2[,6],adjust = 1.5),type="l",lty=4,col=3)
points(density(resultsA2T3[,6],adjust = 1.5),type="l",lty=5,col=4)
points(density(resultsA2T4[,6],adjust = 1.5),type="l",lty=6,col=5)
points(density(resultsA2T5[,6],adjust = 1.5),type="l",lty=7,col=8)
abline(v=parametrosA2[6],col=6)
legend("topright",c("T=500","T=1000","T=1500","T=2000"),lty=c(1,4,5,6,7),col=c(2,3,4,5,6))

plot(density(resultsA2T1[,7],adjust = 1.5),lty=1,col=2,ylim=c(0,1.5),xlab=expression(theta[11]),main="", cex.lab = 1.5)
points(density(resultsA2T2[,7],adjust = 1.5),type="l",lty=4,col=3)
points(density(resultsA2T3[,7],adjust = 1.5),type="l",lty=5,col=4)
points(density(resultsA2T4[,7],adjust = 1.5),type="l",lty=6,col=5)
points(density(resultsA2T5[,7],adjust = 1.5),type="l",lty=7,col=8)
abline(v=parametrosA2[7],col=6)
legend("topright",c("T=500","T=1000","T=1500","T=2000"),lty=c(1,4,5,6,7),col=c(2,3,4,5,6))

plot(density(resultsA2T1[,8],adjust = 1.5),lty=1,col=2,ylim=c(0,10),xlab=expression(gamma),main="", cex.lab = 1.5)
points(density(resultsA2T2[,8],adjust = 1.5),type="l",lty=4,col=3)
points(density(resultsA2T3[,8],adjust = 1.5),type="l",lty=5,col=4)
points(density(resultsA2T4[,8],adjust = 1.5),type="l",lty=6,col=5)
points(density(resultsA2T5[,8],adjust = 1.5),type="l",lty=7,col=8)
abline(v=parametrosA2[8],col=6)
legend("topright",c("T=500","T=1000","T=1500","T=2000"),lty=c(1,4,5,6,7),col=c(2,3,4,5,6))
```



##Eliminating the outlier

```{r}
resultsA2T1<-resultsA2T1[(resultsA2T1[,2]<2 &resultsA2T1[,3]<2),]
resultsA2T2<-resultsA2T2[(resultsA2T2[,2]<2 &resultsA2T2[,3]<2),]
resultsA2T3<-resultsA2T3[(resultsA2T3[,2]<2 &resultsA2T3[,3]<2),]
resultsA2T4<-resultsA2T4[(resultsA2T4[,2]<2 &resultsA2T4[,3]<2),]
resultsA2T5<-resultsA2T5[(resultsA2T5[,2]<2 &resultsA2T5[,3]<2),]
dim(resultsA2T1)
dim(resultsA2T2)
dim(resultsA2T3)
dim(resultsA2T4)
dim(resultsA2T5)
```



```{r}
tablaA2T1<-apply(resultsA2T1,2,mean.sd)
tablaA2T2<-apply(resultsA2T2,2,mean.sd)
tablaA2T3<-apply(resultsA2T3,2,mean.sd)
tablaA2T4<-apply(resultsA2T4,2,mean.sd)
tablaA2T5<-apply(resultsA2T5,2,mean.sd)
tablaA2a<-rbind(tablaA2T1,tablaA2T2,tablaA2T3,tablaA2T4,tablaA2T5)
row.names(tablaA2a)<-c("T1.mean","sd","T2.mean","sd","T3mean","sd","T4mean","sd","T5mean","sd")
round(tablaA2a,4)
parametrosA2
```


```{r}
tablaA2T1<-apply(resultsA2T1,2,kurtosis.skewness)
tablaA2T2<-apply(resultsA2T2,2,kurtosis.skewness)
tablaA2T3<-apply(resultsA2T3,2,kurtosis.skewness)
tablaA2T4<-apply(resultsA2T4,2,kurtosis.skewness)
tablaA2T5<-apply(resultsA2T5,2,kurtosis.skewness)
rownames(tablaA2T1)<-c("kurtosis","skewness")
rownames(tablaA2T2)<-c("kurtosis","skewness")
rownames(tablaA2T3)<-c("kurtosis","skewness")
rownames(tablaA2T4)<-c("kurtosis","skewness")
rownames(tablaA2T5)<-c("kurtosis","skewness")
tablaA2b<-rbind(tablaA2T1,tablaA2T2,tablaA2T3,tablaA2T4,tablaA2T5)
round(tablaA2b,4)
```

Density estimates

```{r,fig.width=10, fig.height=10}
par(mfrow=c(3,3))
plot(density(resultsA2T1[,1],adjust = 1.5),lty=1,col=2,ylim=c(0,6),xlab=expression(alpha),main="", cex.lab = 1.5)
points(density(resultsA2T2[,1],adjust = 1.5),type="l",lty=4,col=3)
points(density(resultsA2T3[,1],adjust = 1.5),type="l",lty=5,col=4)
points(density(resultsA2T4[,1],adjust = 1.5),type="l",lty=6,col=5)
points(density(resultsA2T5[,1],adjust = 1.5),type="l",lty=7,col=8)
abline(v=parametrosA2[1],col=6)
legend("topright",c("T=500","T=1000","T=1500","T=2000"),lty=c(1,4,5,6,7),col=c(2,3,4,5,6))

plot(density(resultsA2T1[,2],adjust = 1.5),lty=1,col=2,ylim=c(0,6),xlab="lambda.p",main="", cex.lab = 1.5)
points(density(resultsA2T2[,2],adjust = 1.5),type="l",lty=4,col=3)
points(density(resultsA2T3[,2],adjust = 1.5),type="l",lty=5,col=4)
points(density(resultsA2T4[,2],adjust = 1.5),type="l",lty=6,col=5)
points(density(resultsA2T5[,2],adjust = 1.5),type="l",lty=7,col=8)
abline(v=parametrosA2[2],col=6)
legend("topright",c("T=500","T=1000","T=1500","T=2000"),lty=c(1,4,5,6,7),col=c(2,3,4,5,6))

plot(density(resultsA2T1[,3],adjust = 1.5),lty=1,col=2,ylim=c(0,6),xlab="lambda.n",main="", cex.lab = 1.5)
points(density(resultsA2T2[,3],adjust = 1.5),type="l",lty=4,col=3)
points(density(resultsA2T3[,3],adjust = 1.5),type="l",lty=5,col=4)
points(density(resultsA2T4[,3],adjust = 1.5),type="l",lty=6,col=5)
points(density(resultsA2T5[,3],adjust = 1.5),type="l",lty=7,col=8)
abline(v=parametrosA2[3],col=6)
legend("topright",c("T=500","T=1000","T=1500","T=2000"),lty=c(1,4,5,6,7),col=c(2,3,4,5,6))

plot(density(resultsA2T1[,4],adjust = 1.5),lty=1,col=2,ylim=c(0,5),xlab=expression(theta[00]),main="", cex.lab = 1.5)
points(density(resultsA2T2[,4],adjust = 1.5),type="l",lty=4,col=3)
points(density(resultsA2T3[,4],adjust = 1.5),type="l",lty=5,col=4)
points(density(resultsA2T4[,4],adjust = 1.5),type="l",lty=6,col=5)
points(density(resultsA2T5[,4],adjust = 1.5),type="l",lty=7,col=8)
abline(v=parametrosA2[4],col=6)
legend("topright",c("T=500","T=1000","T=1500","T=2000"),lty=c(1,4,5,6,7),col=c(2,3,4,5,6))

plot(density(resultsA2T1[,5],adjust = 1.5),lty=1,col=2,ylim=c(0,1.5),xlab=expression(theta[01]),main="", cex.lab = 1.5)
points(density(resultsA2T2[,5],adjust = 1.5),type="l",lty=4,col=3)
points(density(resultsA2T3[,5],adjust = 1.5),type="l",lty=5,col=4)
points(density(resultsA2T4[,5],adjust = 1.5),type="l",lty=6,col=5)
points(density(resultsA2T5[,5],adjust = 1.5),type="l",lty=7,col=8)
abline(v=parametrosA2[5],col=6)
legend("topright",c("T=500","T=1000","T=1500","T=2000"),lty=c(1,4,5,6,7),col=c(2,3,4,5,6))

plot(density(resultsA2T1[,6],adjust = 1.5),lty=1,col=2,ylim=c(0,5),xlab=expression(theta[10]),main="", cex.lab = 1.5)
points(density(resultsA2T2[,6],adjust = 1.5),type="l",lty=4,col=3)
points(density(resultsA2T3[,6],adjust = 1.5),type="l",lty=5,col=4)
points(density(resultsA2T4[,6],adjust = 1.5),type="l",lty=6,col=5)
points(density(resultsA2T5[,6],adjust = 1.5),type="l",lty=7,col=8)
abline(v=parametrosA2[6],col=6)
legend("topright",c("T=500","T=1000","T=1500","T=2000"),lty=c(1,4,5,6,7),col=c(2,3,4,5,6))

plot(density(resultsA2T1[,7],adjust = 1.5),lty=1,col=2,ylim=c(0,1.5),xlab=expression(theta[11]),main="", cex.lab = 1.5)
points(density(resultsA2T2[,7],adjust = 1.5),type="l",lty=4,col=3)
points(density(resultsA2T3[,7],adjust = 1.5),type="l",lty=5,col=4)
points(density(resultsA2T4[,7],adjust = 1.5),type="l",lty=6,col=5)
points(density(resultsA2T5[,7],adjust = 1.5),type="l",lty=7,col=8)
abline(v=parametrosA2[7],col=6)
legend("topright",c("T=500","T=1000","T=1500","T=2000"),lty=c(1,4,5,6,7),col=c(2,3,4,5,6))

plot(density(resultsA2T1[,8],adjust = 1.5),lty=1,col=2,ylim=c(0,10),xlab=expression(gamma),main="", cex.lab = 1.5)
points(density(resultsA2T2[,8],adjust = 1.5),type="l",lty=4,col=3)
points(density(resultsA2T3[,8],adjust = 1.5),type="l",lty=5,col=4)
points(density(resultsA2T4[,8],adjust = 1.5),type="l",lty=6,col=5)
points(density(resultsA2T5[,8],adjust = 1.5),type="l",lty=7,col=8)
abline(v=parametrosA2[8],col=6)
legend("topright",c("T=500","T=1000","T=1500","T=2000"),lty=c(1,4,5,6,7),col=c(2,3,4,5,6))
```






For t=500:

```{r,fig.width=15, fig.height=15}
par(mfrow=c(3,3))
for(i in 1:3){
  hist(resultsA2T1[,i],freq=FALSE,xlab=expression(theta[i]),main="", cex.lab = 1.5,breaks=20)
  abline(v=parametrosA2[i],col=3)
  curve(dnorm(x,mean(resultsA2T1[,i]),sd(resultsA2T1[,i])),add=T,col=2)
  qqPlot(resultsA2T1[,i])
  boxplot(resultsA2T1[,i])
}
```

For t=1000:
  
```{r,fig.width=15, fig.height=15}
par(mfrow=c(3,3))
for(i in 1:3){
  hist(resultsA2T2[,i],freq=FALSE,xlab=expression(theta[i]),main="", cex.lab = 1.5,breaks=20)
  abline(v=parametrosA2[i],col=3)
  curve(dnorm(x,mean(resultsA2T2[,i]),sd(resultsA2T2[,i])),add=T,col=2)
  qqPlot(resultsA2T2[,i])
  boxplot(resultsA2T2[,i])
}
```

For t=1500:
  
```{r,fig.width=15, fig.height=15}
par(mfrow=c(3,3))
for(i in 1:3){
  hist(resultsA2T3[,i],freq=FALSE,xlab=expression(theta[i]),main="", cex.lab = 1.5,breaks=20)
  abline(v=parametrosA2[i],col=3)
  curve(dnorm(x,mean(resultsA2T3[,i]),sd(resultsA2T3[,i])),add=T,col=2)
  qqPlot(resultsA2T3[,i])
  boxplot(resultsA2T3[,i])
}
```

For t=2000:
  
```{r,fig.width=15, fig.height=15}
par(mfrow=c(3,3))
for(i in 1:3){
  hist(resultsA2T4[,i],freq=FALSE,xlab=expression(theta[i]),main="", cex.lab = 1.5,breaks=20)
  abline(v=parametrosA2[i],col=3)
  curve(dnorm(x,mean(resultsA2T4[,i]),sd(resultsA2T4[,i])),add=T,col=2)
  qqPlot(resultsA2T4[,i])
  boxplot(resultsA2T4[,i])
}
```
For t=3000:
  
```{r,fig.width=15, fig.height=15}
par(mfrow=c(3,3))
for(i in 1:3){
  hist(resultsA2T5[,i],freq=FALSE,xlab=expression(theta[i]),main="", cex.lab = 1.5,breaks=20)
  abline(v=parametrosA2[i],col=3)
  curve(dnorm(x,mean(resultsA2T5[,i]),sd(resultsA2T5[,i])),add=T,col=2)
  qqPlot(resultsA2T5[,i])
  boxplot(resultsA2T5[,i])
}
```





## Scenario 3

$\alpha=0.7$,\
$\lambda_+=1$,\
$\lambda_-=0.5$,\
$\theta_{a0}=-0.3$\
$\theta_{a1}=0.8$\
$\theta_{b0}=0.5$\
$\theta_{b1}=-0.1$\
$\gamma=1$.\


##Eliminating the outlier

```{r}
resultsA3T1<-resultsA3T1[(resultsA3T1[,2]<2 &resultsA3T1[,3]<2),]
resultsA3T2<-resultsA3T2[(resultsA3T2[,2]<2 &resultsA3T2[,3]<2),]
resultsA3T3<-resultsA3T3[(resultsA3T3[,2]<2 &resultsA3T3[,3]<2),]
resultsA3T4<-resultsA3T4[(resultsA3T4[,2]<2 &resultsA3T4[,3]<2),]
resultsA3T5<-resultsA3T5[(resultsA3T5[,2]<2 &resultsA3T5[,3]<2),]
dim(resultsA3T1)
dim(resultsA3T2)
dim(resultsA3T3)
dim(resultsA3T4)
dim(resultsA3T5)
```

```{r}
tablaA3T1<-apply(resultsA3T1,2,mean.sd)
tablaA3T2<-apply(resultsA3T2,2,mean.sd)
tablaA3T3<-apply(resultsA3T3,2,mean.sd)
tablaA3T4<-apply(resultsA3T4,2,mean.sd)
tablaA3T5<-apply(resultsA3T5,2,mean.sd)
tablaA3a<-rbind(tablaA3T1,tablaA3T2,tablaA3T3,tablaA3T4,tablaA3T5)
row.names(tablaA3a)<-c("T1.mean","sd","T2.mean","sd","T3mean","sd","T4mean","sd","T5mean","sd")
round(tablaA3a,4)
parametrosA3
```


```{r}
tablaA3T1<-apply(resultsA3T1,2,kurtosis.skewness)
tablaA3T2<-apply(resultsA3T2,2,kurtosis.skewness)
tablaA3T3<-apply(resultsA3T3,2,kurtosis.skewness)
tablaA3T4<-apply(resultsA3T4,2,kurtosis.skewness)
tablaA3T5<-apply(resultsA3T5,2,kurtosis.skewness)
rownames(tablaA3T1)<-c("kurtosis","skewness")
rownames(tablaA3T2)<-c("kurtosis","skewness")
rownames(tablaA3T3)<-c("kurtosis","skewness")
rownames(tablaA3T4)<-c("kurtosis","skewness")
rownames(tablaA3T5)<-c("kurtosis","skewness")
tablaA3b<-rbind(tablaA3T1,tablaA3T2,tablaA3T3,tablaA3T4,tablaA3T5)
round(tablaA3b,4)
```

Density estimates

```{r,fig.width=10, fig.height=10}
par(mfrow=c(3,3))
plot(density(resultsA3T1[,1],adjust = 1.5),lty=1,col=2,ylim=c(0,6),xlab=expression(alpha),main="", cex.lab = 1.5)
points(density(resultsA3T2[,1],adjust = 1.5),type="l",lty=4,col=3)
points(density(resultsA3T3[,1],adjust = 1.5),type="l",lty=5,col=4)
points(density(resultsA3T4[,1],adjust = 1.5),type="l",lty=6,col=5)
points(density(resultsA3T5[,1],adjust = 1.5),type="l",lty=7,col=8)
abline(v=parametrosA3[1],col=6)
legend("topright",c("T=500","T=1000","T=1500","T=2000"),lty=c(1,4,5,6,7),col=c(2,3,4,5,6))

plot(density(resultsA3T1[,2],adjust = 1.5),lty=1,col=2,ylim=c(0,4),xlab="lambda.p",main="", cex.lab = 1.5)
points(density(resultsA3T2[,2],adjust = 1.5),type="l",lty=4,col=3)
points(density(resultsA3T3[,2],adjust = 1.5),type="l",lty=5,col=4)
points(density(resultsA3T4[,2],adjust = 1.5),type="l",lty=6,col=5)
points(density(resultsA3T5[,2],adjust = 1.5),type="l",lty=7,col=8)
abline(v=parametrosA3[2],col=6)
legend("topright",c("T=500","T=1000","T=1500","T=2000"),lty=c(1,4,5,6,7),col=c(2,3,4,5,6))

plot(density(resultsA3T1[,3],adjust = 1.5),lty=1,col=2,ylim=c(0,4),xlab="lambda.n",main="", cex.lab = 1.5)
points(density(resultsA3T2[,3],adjust = 1.5),type="l",lty=4,col=3)
points(density(resultsA3T3[,3],adjust = 1.5),type="l",lty=5,col=4)
points(density(resultsA3T4[,3],adjust = 1.5),type="l",lty=6,col=5)
points(density(resultsA3T5[,3],adjust = 1.5),type="l",lty=7,col=8)
abline(v=parametrosA3[3],col=6)
legend("topright",c("T=500","T=1000","T=1500","T=2000"),lty=c(1,4,5,6,7),col=c(2,3,4,5,6))

plot(density(resultsA3T1[,4],adjust = 1.5),lty=1,col=2,ylim=c(0,6),xlab=expression(theta[00]),main="", cex.lab = 1.5)
points(density(resultsA3T2[,4],adjust = 1.5),type="l",lty=4,col=3)
points(density(resultsA3T3[,4],adjust = 1.5),type="l",lty=5,col=4)
points(density(resultsA3T4[,4],adjust = 1.5),type="l",lty=6,col=5)
points(density(resultsA3T5[,4],adjust = 1.5),type="l",lty=7,col=8)
abline(v=parametrosA3[4],col=6)
legend("topright",c("T=500","T=1000","T=1500","T=2000"),lty=c(1,4,5,6,7),col=c(2,3,4,5,6))

plot(density(resultsA3T1[,5],adjust = 1.5),lty=1,col=2,ylim=c(0,3),xlab=expression(theta[01]),main="", cex.lab = 1.5)
points(density(resultsA3T2[,5],adjust = 1.5),type="l",lty=4,col=3)
points(density(resultsA3T3[,5],adjust = 1.5),type="l",lty=5,col=4)
points(density(resultsA3T4[,5],adjust = 1.5),type="l",lty=6,col=5)
points(density(resultsA3T5[,5],adjust = 1.5),type="l",lty=7,col=8)
abline(v=parametrosA3[5],col=6)
legend("topright",c("T=500","T=1000","T=1500","T=2000"),lty=c(1,4,5,6,7),col=c(2,3,4,5,6))

plot(density(resultsA3T1[,6],adjust = 1.5),lty=1,col=2,ylim=c(0,6),xlab=expression(theta[10]),main="", cex.lab = 1.5)
points(density(resultsA3T2[,6],adjust = 1.5),type="l",lty=4,col=3)
points(density(resultsA3T3[,6],adjust = 1.5),type="l",lty=5,col=4)
points(density(resultsA3T4[,6],adjust = 1.5),type="l",lty=6,col=5)
points(density(resultsA3T5[,6],adjust = 1.5),type="l",lty=7,col=8)
abline(v=parametrosA3[6],col=6)
legend("topright",c("T=500","T=1000","T=1500","T=2000"),lty=c(1,4,5,6,7),col=c(2,3,4,5,6))

plot(density(resultsA3T1[,7],adjust = 1.5),lty=1,col=2,ylim=c(0,3),xlab=expression(theta[11]),main="", cex.lab = 1.5)
points(density(resultsA3T2[,7],adjust = 1.5),type="l",lty=4,col=3)
points(density(resultsA3T3[,7],adjust = 1.5),type="l",lty=5,col=4)
points(density(resultsA3T4[,7],adjust = 1.5),type="l",lty=6,col=5)
points(density(resultsA3T5[,7],adjust = 1.5),type="l",lty=7,col=8)
abline(v=parametrosA3[7],col=6)
legend("topright",c("T=500","T=1000","T=1500","T=2000"),lty=c(1,4,5,6,7),col=c(2,3,4,5,6))

plot(density(resultsA3T1[,8],adjust = 1.5),lty=1,col=2,ylim=c(0,10),xlab=expression(gamma),main="", cex.lab = 1.5)
points(density(resultsA3T2[,8],adjust = 1.5),type="l",lty=4,col=3)
points(density(resultsA3T3[,8],adjust = 1.5),type="l",lty=5,col=4)
points(density(resultsA3T4[,8],adjust = 1.5),type="l",lty=6,col=5)
points(density(resultsA3T5[,8],adjust = 1.5),type="l",lty=7,col=8)
abline(v=parametrosA3[8],col=6)
legend("topright",c("T=500","T=1000","T=1500","T=2000"),lty=c(1,4,5,6,7),col=c(2,3,4,5,6))
```


For t=500:
  
```{r,fig.width=15, fig.height=15}
par(mfrow=c(3,3))
for(i in 1:3){
  hist(resultsA3T1[,i],freq=FALSE,xlab=expression(theta[i]),main="", cex.lab = 1.5,breaks=20)
  abline(v=parametrosA3[i],col=3)
  curve(dnorm(x,mean(resultsA3T1[,i]),sd(resultsA3T1[,i])),add=T,col=2)
  qqPlot(resultsA3T1[,i])
  boxplot(resultsA3T1[,i])
}
```

For t=1000:
  
```{r,fig.width=15, fig.height=15}
par(mfrow=c(3,3))
for(i in 1:3){
  hist(resultsA3T2[,i],freq=FALSE,xlab=expression(theta[i]),main="", cex.lab = 1.5,breaks=20)
  abline(v=parametrosA3[i],col=3)
  curve(dnorm(x,mean(resultsA3T2[,i]),sd(resultsA3T2[,i])),add=T,col=2)
  qqPlot(resultsA3T2[,i])
  boxplot(resultsA3T2[,i])
}
```

For t=1500:
  
```{r,fig.width=15, fig.height=15}
par(mfrow=c(3,3))
for(i in 1:3){
  hist(resultsA3T3[,i],freq=FALSE,xlab=expression(theta[i]),main="", cex.lab = 1.5,breaks=20)
  abline(v=parametrosA3[i],col=3)
  curve(dnorm(x,mean(resultsA3T3[,i]),sd(resultsA3T3[,i])),add=T,col=2)
  qqPlot(resultsA3T3[,i])
  boxplot(resultsA3T3[,i])
}
```

For t=2000:
  
```{r,fig.width=15, fig.height=15}
par(mfrow=c(3,3))
for(i in 1:3){
  hist(resultsA3T4[,i],freq=FALSE,xlab=expression(theta[i]),main="", cex.lab = 1.5,breaks=20)
  abline(v=parametrosA3[i],col=3)
  curve(dnorm(x,mean(resultsA3T4[,i]),sd(resultsA3T4[,i])),add=T,col=2)
  qqPlot(resultsA3T4[,i])
  boxplot(resultsA3T4[,i])
}
```
For t=3000:
  
```{r,fig.width=15, fig.height=15}
par(mfrow=c(3,3))
for(i in 1:3){
  hist(resultsA3T5[,i],freq=FALSE,xlab=expression(theta[i]),main="", cex.lab = 1.5,breaks=20)
  abline(v=parametrosA3[i],col=3)
  curve(dnorm(x,mean(resultsA3T5[,i]),sd(resultsA3T5[,i])),add=T,col=2)
  qqPlot(resultsA3T5[,i])
  boxplot(resultsA3T5[,i])
}
```